Split `r paste(params$species)` biomass by maturity class

### 2020-02-19 analysis/VOCC/1-split-biomass-by-maturity.Rmd
add options for changing ogive threshold and overriding maturity split to maturity rmd

---
title: "Split `r paste(params$species)` biomass by maturity class"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document
params: 
    species: "Longnose Skate"
    #species:"Redbanded Rockfish"
    #species: "Pacific Ocean Perch"
    region: "All synoptic surveys"
    # region: "Both odd year surveys"
    split: FALSE
---

```{r global_options, include=FALSE}
species <- params$species
region <- params$region
split <- params$split

>>>>

---
title: "Split `r paste(params$species)` biomass by maturity class"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document
params: 
    #species: "Bocaccio"
    species: "Threadfin Sculpin"
    #species: "Quillback Rockfish"
    #species: "Yelloweye Rockfish"
    #species: "Shortraker Rockfish"
    # species: "Pacific Ocean Perch"
    region: "All synoptic surveys"
    # region: "Both odd year surveys"
    threshold: 0.05
    split: FALSE
---

```{r global_options, include=FALSE}
species <- params$species
region <- params$region
split <- params$split
threshold <- params$threshold
